---
title: "Data606 Project Proposal"
author: "Ritesh Lohiya"
date: "March 31, 2018"
output: html_document
---

Load Libraries:

```{r}
library(knitr)
library(stringr)
library(tidyr)
library(dplyr)
library(ggplot2)
```

### Data Preparation

```{r}
movies_2008 <- read.csv("https://raw.githubusercontent.com/Riteshlohiya/Data606_Project_Proposal/master/movies_2008_V1.csv", sep=",")
head(movies_2008)
```


### Research question 

The data is collected from StatCrunch and has the details of movie released in 2008. In this study we will see if the genre and RotTom(Rotten Tomatoes ratings) of a movie has any affect on the gross collection.


### Cases 

```{r}
dim(movies_2008)
```

Each case represents the movie details. The dataset has 227 observations.

### Data collection 

The data is collected from StatCrunch website link for which is given below. The RomTom ratings are taken from Rotten Tomatoes. The collected data is then stored in GitHub repository: https://raw.githubusercontent.com/Riteshlohiya/Data606_Project_Proposal/master/movies_2008_V1.csv

Link for StatCrunch: https://www.statcrunch.com/app/index.php?dataid=398031
Link for Rotten Tomatoes ratings: https://www.kaggle.com/tmdb/tmdb-movie-metadata/data

### Type of study 

This is an observational study.

### Data Source 

The data is from StatCrunch website link for which is given below. The RomTom ratings are taken from Rotten Tomatoes.

Link for StatCrunch: https://www.statcrunch.com/app/index.php?dataid=398031
Link for Rotten Tomatoes ratings: https://www.kaggle.com/tmdb/tmdb-movie-metadata/data

### Response 

Gross Collection(Gross_Collection) is the response variable which is numerical. 

### Explanatory 

Genre is the explanatory variable which is categorical. RotTom is another explanatory variable which is numerical ordinal.

### Relevant summary statistics

```{r}
movies_2008 <- as.data.frame(movies_2008) 
summary(movies_2008)
```

```{r}
movies_Genre <- table(movies_2008$Genre) 
```

```{r}
par(oma = c(1,1,1,1))
par(mar = c(4,5,2,1))
barplot(movies_Genre[order(movies_Genre)],
        horiz = TRUE,
        las = 1,
        col = c(rainbow(6)),
        border = NA,
        main = "Frequency of Movie Genre",
        xlab = "Count",
        font.lab = 2,
        cex.names = 0.75)
        
```

#Genre Boxplot:

```{r}
ggplot(movies_2008,aes(x=Genre,y=Gross_Collection)) + geom_boxplot()
```

#RotTom Ratings Histogram:

```{r}
ggplot(movies_2008, aes(x=RotTom)) + geom_histogram()
```

#Summary of the data for Gross_Collection by Genre:

```{r}
movies_2008_Gross_Collection  <- movies_2008 %>% 
  group_by(Genre) 

movies_2008_Gross_Collection <- summarise(
  movies_2008_Gross_Collection,
  count = n(),
  mean_collection = mean(Gross_Collection),
  sd_collection = sd(Gross_Collection),
  max_collection = max(Gross_Collection)
  
)

movies_2008_Gross_Collection
```

#Summary of the data for RotTom Ratings by Genre:

```{r}
movies_2008_RotTom  <- movies_2008 %>% 
  group_by(Genre) 

movies_2008_RotTom <- summarise(
  movies_2008_RotTom,
  count = n(),
  mean_RotTom = mean(RotTom),
  sd_RotTom = sd(RotTom),
  max_RotTom= max(RotTom)
  
)

movies_2008_RotTom
```







