---
title: "Data606 Project Proposal"
author: "Ritesh Lohiya"
date: "March 31, 2018"
output: html_document
---

Load Libraries:

```{r}
library(knitr)
library(stringr)
library(tidyr)
library(dplyr)
library(ggplot2)
```

### Data Preparation

```{r}
movies_2008 <- read.csv("https://raw.githubusercontent.com/Riteshlohiya/Data606_Project_Proposal/master/movies_2008.csv", sep=",")
head(movies_2008)
```


### Research question 

The data is collected from StatCrunch and has the details of movie released in 2008. In this study we will see if the genre of a movie has any affect on the gross collection.


### Cases 

Each case represents the movie details. The dataset has 734 observations.

### Data collection 

The data is collected from StatCrunch website link for which is given below. The collected data is then stored in GitHub repository: https://raw.githubusercontent.com/Riteshlohiya/Data606_Project_Proposal/master/movies_2008.csv

Link for data: https://www.statcrunch.com/app/index.php?dataid=398031

### Type of study 

This is an observational study.

### Data Source 

The data is from StatCrunch website link for which is given below.

Link: https://www.statcrunch.com/app/index.php?dataid=398031

### Response 

Gross Collection(Gross_Collection) is the response variable which is numerical. 

### Explanatory 

Genre is the explanatory variable which is categorical.

### Relevant summary statistics

```{r}
movies_2008 <- as.data.frame(movies_2008) 
summary(movies_2008)
```

```{r}
ggplot(movies_2008,aes(x=Genre,y=Gross_Collection)) + geom_boxplot()
```

Summary of the data:

```{r}
movies_2008  <- movies_2008 %>% 
  group_by(Genre) 

movies_2008 <- summarise(
  movies_2008,
  count = n(),
  mean_collection = mean(Gross_Collection),
  sd_collection = sd(Gross_Collection),
  max_collection = max(Gross_Collection)
  
)

movies_2008
```



